%% start of file `template_en.tex'.
%% Copyright 2007 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt]{moderncv}

% moderncv themes
\moderncvtheme[blue]{casual}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[green]{casual}                % idem

% character encoding
%\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.85]{geometry}
\usepackage[usenames,dvipsnames]{color}
\usepackage{hyperref}
\hypersetup{
  colorlinks,
  citecolor=Violet,
  linkcolor=Red,
  urlcolor=Blue}
\recomputelengths                             % required when changes are made to page layout lengths
\usepackage{ifpdf}

% personal data
\firstname{Joshua}
\familyname{Grant}
%\title{Curriculum Vitae}               % optional, remove the line if not wanted
\address{29 Symons St}{Toronto, Ontario M8V 1T7}    % optional, remove the line if not wanted
\mobile{Mobile: (647) 240-0961}                      % optional, remove the line if not wanted
\email{joshua.m.grant@gmail.com}                      % optional, remove the line if not wanted
\email{Twitter: @joshin4colours}
%\extrainfo{additional information (optional)} % optional, remove the line if not wanted
%\photo[64pt]{my_photo_smaller}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{"A mathematician is a machine for turning coffee into theorems." -- Alfr\'ed R\'enyi}                 % optional, remove the line if not wanted

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Education}
\cventry{2007-2009}{MSc - Applied Mathematics}{The University of Western Ontario}{London}{Ontario}{Research area: Mathematical Biology}  % arguments 3 to 6 are optional
\cventry{2003-2007}{BSc - Mathematics}{Trent University}{Peterborough}{Ontario}{Dean's Honour List, 2003-2007}  % arguments 

\section{Experience}
\cventry{December 2015--Present}{Contributing Author}{Techwell Publications}{Toronto}{Ontario}{I've written one article as a paid contributor to Sticky Minds, a software testing publication. My first article was called "What Flaky Tests Can Tell You", published in February 2016.}
\cventry{October 2010--Present}{Test Developer}{CaseWare International}{Toronto}{Ontario}{I am an automated tester for CaseWare's cloud-based products. I write and maintain automated regression and acceptance tests, emphasizing maintainability in my test code. Currently, I write JavaScript Selenium-tests for SE, CaseWare's audit platform, and am exploring ways to make functional and user acceptance tests more efficient.}                % arguments 3 to 6 are optional
\cventry{August 2009--August 2010}{Research Associate}{Cerebral Diagnostics Canada, Inc}{Toronto}{Ontario}{I was a scientific and technical researcher working for this small biotechnology star-up. We focused on several projects, including developing in-house software for research in EEG (Electroencephalography) and conducting EEG-based studies in pain research.}                % arguments 3 to 6 are optional
\cventry{2007--2009}{Teaching Assistant}{The University of Western Ontario}{London}{Ontario}{I lead tutorials and drop-in help sessions for students, graded tests and assignments and held regular office hours for additional student help.}                % arguments 3 to 6 are optional
\cventry{Summer 2006}{Research Assistant, Department of Mathematics}{Trent University}{Peterborough}{Ontario}{I designed and developed a database of corporate ownership based on SEC filings using Perl and CGI.}                % arguments 3 to 6 are optional
\cventry{2005--2006}{Teaching Assistant}{Trent University}{Peterborough}{Ontario}{I assisted students in a lab-based physics for education students course. Mainly, my goal was help them understand the physical concepts and gain an appreciation for physics.}                % arguments 3 to 6 are optional
%\subsection{Miscellaneous}
%\cventry{year--year}{Job title}{Employer}{City}{}{Description line 1\newline{}Description line 2}% arguments 3 to 6 are optional

\section{What I'm Looking For:}
\cvlistitem{Opportunities involving coding and automation techniques}
\cvlistitem{Data Science-based roles with quantitative or mathematical focus}
\cvlistitem{Opportunities to work in a data-driven/data-oriented environment}
\cvlistitem{Roles encouraging collaboration between teams}
\cvlistitem{Any role that allows me to improve and expand my programming knowledge, with new or familiar languages and tools}
%\section{Strengths and Skills}
%\cvlistitem{Strong personal and technical communication skills}
%\cvlistitem{Ability to interact and work in variety of settings and with various personalities}
%\cvlistitem{Exceptional problem solving skills}
%\cvlistitem{Experience with individual-based and Monte Carlo simulation}
%\cvlistitem{Knowledge and experience in object-oriented programming}
%\cvlistitem{Experience with statistical and data analysis in non-academic settings, including non-parametric statistics and stochastic processes}

\section{Tools I've Used} 
\cvlistitem{Languages - Java, Python, JavaScript with NodeJS}
\cvlistitem{Software Tools - Eclipse, Git, Atlassian JIRA and Stash, WebStorm IDE, Jenkins CI}
\cvlistitem{Quantitative Tools  - MATLAB, SciPy and NumPy, Monte Carlo Simulation in C}
%\cvcomputer{}{} {}{}

\section{Interests}
\cvline{Linux}{Making the most out of my operating system. If only more things were text-based.}
\cvline{Cooking}{It's really just the love of food. My favourite dishes I've prepared include salt-block seared tuna and pulled pork.}
\cvline{Doing Stuff Online}{Testing is great, along with other things digital. My blog is Simply the Test (simplythetest.tumblr.com)}

\section{References}
\cventry{Ron Perreault}{Department Head}{Test Developmet}{CaseWare International}{(416) 867-9504 x1280}{ron.perreault@caseware.com}
\cventry{Brendan Looker}{Team Lead, Web}{Test Developmet}{CaseWare International}{(416) 867-9504 x1184}{brendan.looker@caseware.com}
\cventry{Dr Lindi Wahl}{Professor}{Department of Applied Mathematics}{The University of Western Ontario}{(519) 661-2111 ext 88795}{lwahl@uwo.ca}
\cventry{Dr Geoff Wild}{Professor}{Department of Applied Mathematics}{The University of Western Ontario}{(519) 661-2111 ext 88784}{gwild@uwo.ca} 
%\cventry{Dr Albert Ler}{Research Associate}{Cerebral Diagnostics Canada Inc}{alersh@gmail.com}
%\cventry{$\cdot$}{Dr Marcus Pivato}{Professor}{Department of Mathematics}{Trent University}{(705) 748-1011 ext 7293}{pivato@xaravve.trentu.ca}

%\section{Extra 1}
%\cvlistitem{Item 1}
%\cvlistitem{Item 2}
%\cvlistitem[+]{Item 3}            % optional other symbol

%\section{Extra 2}
%\cvlistdoubleitem[\Neutral]{Item 1}{Item 4}
%\cvlistdoubleitem[\Neutral]{Item 2}{Item 5}
%cvlistdoubleitem[\Neutral]{Item 3}{}

% Publications from a BibTeX file
%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{publications}       % 'publications' is the name of a BibTeX file
\end{document}


%% end of file `template_en.tex'.
