%% start of file `template_en.tex'.
%% Copyright 2007 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt]{moderncv}

% moderncv themes
\moderncvtheme[blue]{casual}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
% \moderncvtheme[green]{casual}                % idem

% character encoding
%\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.85]{geometry}
\usepackage[usenames,dvipsnames]{color}
\usepackage{hyperref}
\hypersetup{
  colorlinks,
  citecolor=Violet,
  linkcolor=Red,
  urlcolor=Blue}
\recomputelengths                             % required when changes are made to page layout lengths
\usepackage{ifpdf}

% personal data
\firstname{Joshua}
\familyname{Grant}
%\title{Curriculum Vitae}               % optional, remove the line if not wanted
\address{29 Symons St}{Toronto, Ontario M8V 1T7}    % optional, remove the line if not wanted
\mobile{Mobile: (647) 240-0961}                      % optional, remove the line if not wanted
\email{joshua.m.grant@gmail.com}                      % optional, remove the line if not wanted
\email{https://joshgrant.online}
%\extrainfo{additional information (optional)} % optional, remove the line if not wanted
%\photo[64pt]{my_photo_smaller}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{"A mathematician is a machine for turning coffee into theorems." -- Alfr\'ed R\'enyi}                 % optional, remove the line if not wanted

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Relevant Experience}
\cventry{October 2022--May 2023}{Developer Advocate}{Code Intelligence}{Bonn/Remote}{Germany/Canada}{As a developer advocate at an early-stage start up, I focused on outreach and education, creating Java-based examples for CI Fuzz, a DAST fuzz testing tool.}                % arguments 3 to 6 are optional
\cventry{April 2017--February 2018}{Test Developer}{JUICE Mobile}{Toronto}{Ontario}{I worked with a programmatic advertisting platform, primarily developing a service-level or API test framework. I worked on a team of 10 developers as an "embedded" test development specialist.}                % arguments 3 to 6 are optional
\cventry{October 2010--October 2016}{Test Developer}{CaseWare International}{Toronto}{Ontario}{I worked primarily with the CaseWare Time product. I wrote and maintained automated regression and acceptance tests, emphasizing maintainability in my test code. This included working with Java-based Selenium tests for Time on the Go, Time's web-based version and SilkTest suites for Time, the primary desktop product.}                % arguments 3 to 6 are optional
%\subsection{Miscellaneous}
%\cventry{year--year}{Job title}{Employer}{City}{}{Description line 1\newline{}Description line 2}% arguments 3 to 6 are optional

\section{Education}
\cventry{2007-2009}{MSc - Applied Mathematics}{The University of Western Ontario}{London}{Ontario}{Research area: Mathematical Biology}  % arguments 3 to 6 are optional
\cventry{2003-2007}{BSc - Mathematics}{Trent University}{Peterborough}{Ontario}{Dean's Honour List, 2003-2007}  % arguments 

\section{What I'm Looking For:}
\cvlistitem{Test Automation and Architecture: I've worked at all levels of the test automation pyramid and would like to continue to do so}
\cvlistitem{Java: I have worked on several projects using Java, becoming proficient with both Java language programming and the Java tool ecosystem}
\cvlistitem{Application Security: Helping application developers and teams find and triage security issues quickly and as early as possible, and building the tools for developers to do so}
\cvlistitem{Championing Quality: Working with and coding with other team members, between and within teams}
\cvlistitem{Working with Systems at Scale: Scaling and maintaining large systems is an interest of mine from a quality point of view}
%\section{Strengths and Skills}
%\cvlistitem{Strong personal and technical communication skills}
%\cvlistitem{Ability to interact and work in variety of settings and with various personalities}
%\cvlistitem{Excellent problem solving skills}
%\cvlistitem{Strengths in project planning and abstracting reasoning}
%\cvlistitem{Experience with individual-based and Monte Carlo simulation}
%\cvlistitem{Knowledge and experience in object-oriented programming}
%\cvlistitem{Experience with statistical and data analysis in non-academic settings, including non-parametric statistics and stochastic processes}

\section{Tools I Love} 
\cvlistitem{Java, for professional software development}
\cvlistitem{CI Fuzz, for cross-language fuzz testing}
\cvlistitem{Postman, for API testing and exploration}
\cvlistitem{Selenium, for automating web applications, for testing and otherwise}
\cvlistitem{JetBrains, for Java development in IntelliJ}
\cvlistitem{Camtasia, for creating captivating video content}
\cvlistitem{Taking short walks along the lake, for excellent debugging}

\newpage

\section{What I've Done, in Chronological Order}
\cvlistitem{Built and maintained a medium-large Java-based test framework for a project management web application of approximately 1000 tests. This framework used Selenium with TestNG and achieved partial parallelization.}
\cvlistitem{Built a unit test suite for an open source project called Proselint, writing approximately 50 tests as a basis for testing in that project.}
\cvlistitem{Built an API test framework for a programmatic ad platform product. This tested the API layer of the internal application using approximately 200 tests.}
\cvlistitem{Contributed to example Java projects at both Sauce Labs and Code Intelligence}
\cvlistitem{Designed and delivered a standard presentation on best practices in Continous Integration/Continous Deployment. This presentation was delivered as part of solution architech work to enterprise company customers such as Accenture and at tech conferences such as Targeting Quality by KWSQA.}
\cvlistitem{Designed and delivered a presentation called "What the Fuzz? An Introduction to Fuzz Testing". This talk was delivered at multiple meetups including PyLadies Toronto and BSides Rochester.}

\section{Interests}
\cvline{Food}{I enjoy eating and cooking food of all kinds. Currently living in Toronto which an excellent food city overall.}
\cvline{Art}{Current interests include work by Agnes Martin and Louis Kahn.}
\cvline{Being Online}{I am quite active on social media, including Twitter \emph{@joshin4colours} and Mastodon \emph{mastodon.social/@joshin4colours} }

% \section{References}
% \cventry{Khaled Yakdan}{Co-Founder and Chief Scientist}{Code Intelligence}{yakdan@code-intelligence.com}
% \cventry{Evelyn Coleman}{Manager, Implementation Engineering}{Sauce Labs}{coleve27@gmail.com}
% \cventry{Marion Nehring}{Director, Developer Relations}{Code Intelligence}{marion.nehring@outlook.com} 
% \cventry{Nikolay Advolodkin}{Senior Developer Advocate}{Sauce Labs}{nadvolod@gmail.com}
%\cventry{$\cdot$}{Dr Marcus Pivato}{Professor}{Department of Mathematics}{Trent University}{(705) 748-1011 ext 7293}{pivato@xaravve.trentu.ca}

%\section{Extra 1}
%\cvlistitem{Item 1}
%\cvlistitem{Item 2}
%\cvlistitem[+]{Item 3}            % optional other symbol

%\section{Extra 2}
%\cvlistdoubleitem[\Neutral]{Item 1}{Item 4}
%\cvlistdoubleitem[\Neutral]{Item 2}{Item 5}
%cvlistdoubleitem[\Neutral]{Item 3}{}

% Publications from a BibTeX file
%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{publications}       % 'publications' is the name of a BibTeX file
\end{document}


%% end of file `template_en.tex'.
